### 2022-02-17 appendix_properties_of_B/appendix.tex
typos

	T_{ii}\bs I_{N_0} + c_i\bs P_0^{-1}(\bs F_i^{00}+\bs G_0)\bs M_0^{-1}\bs P_0 & i = j, \\
T_{ij}\bs I_{N_0} - c_ip_{ij}^{-1} 1(c_i<0)\bs F_i^{00}\bs M_0^{-1}\bs P_0 & i \neq j,

@@

	T_{ii}\bs I_{N_K} + c_i\bs P_K^{-1}(\bs F_i^{KK}+\bs G_K)\bs M_K^{-1}\bs P_K & i = j, \\
T_{ij}\bs I_{N_K} + c_ip_{ij}^{K+1} 1(c_i>0)\bs P_K^{-1}\bs F_i^{KK}\bs M_K^{-1}\bs P_K & i \neq j,

@@

\begin{lem}
	If \(\{\phi^r_k(x)\}_{r\in\{1,...,p_k\}}\), are chosen as the Lagrange interpolating polynomials on \(\mathcal D_k\), \(k\in\mathcal K^\circ\), then the matrix \( {  {\mathfrak{\bs B}}}\) has zero row-sums. 
\end{lem}
\begin{proof}
	First we make numerous algebraic observations. Let \(\boldsymbol 1\) and \(\boldsymbol 0\) be column vectors of ones and zeros, respectively, with an appropriate length depending on the context. Using Property 1, observe that 
	\begin{align*}
        \bs M_k\boldsymbol 1 &= \left(\sum_{s=1}^{p_k} \int_{x\in\calD_k}\phi^r_k(x)\phi_s^k(x)\wrt x\right)_{r\in\{1,...,p_k\}}\tr{}
	%
        \\&= \left(\int_{x\in\calD_k}\phi^r_k(x)\sum_{s=1}^{p_k} \phi_s^k(x)\wrt x \right)_{r\in\{1,...,p_k\}} \tr{}
        %
        \\&= \left(\int_{x\in\calD_k}\phi^r_k(x)\wrt x\right)_{r\in\{1,...,p_k\}} \tr{}
        %
        \\&= \bs P_k\boldsymbol 1,
	\end{align*}
	hence \(\bs M_k^{-1}\bs P_k\boldsymbol 1=\boldsymbol 1\). Also, 
	\begin{align*}
        \bs G_k\bs M_k^{-1}\bs P_k\boldsymbol 1 = \bs G_k\boldsymbol 1 &= \left(\sum_{s=1}^{p_k} \int_{x\in\calD_k}\phi^r_k(x)\cfrac{\wrt }{\wrt x}\phi_k^s(x)\wrt x\right)_{r\in\{1,...,p_k\}} \tr{}
	%
        \\&= \left(\int_{x\in\calD_k}\phi^r_k(x)\cfrac{\wrt }{\wrt x}\sum_{s=1}^{p_k} \phi_k^s(x)\wrt x \right)_{r\in\{1,...,p_k\}} \tr{}
	%
        \\&= \left(\int_{x\in\calD_k}\phi^r_k(x)\cfrac{\wrt }{\wrt x}1\wrt x\right)_{r\in\{1,...,p_k\}} \tr{}
	%
        \\&= \boldsymbol 0,
	\end{align*}
	where we have again used Property 1. Consider \(c_i>0\) and let \(\boldsymbol b\) and \(\boldsymbol d\) be arbitrary row-vectors of length \(p_k\) and \(p_{k+1}\), respectively. By Property 2, for \(k\in\mathcal K^\circ,\)
	\begin{align*}
        \bs F_i^{kk}\boldsymbol b &= -\boldsymbol \phi_k(y_{k+1})\tr{} \boldsymbol \phi_k(y_{k+1})\boldsymbol b \\&= -(\bs e^k_{p_k})\tr{} \bs e_{p_k}^k\bs b \\&= -b_{p_k}(\boldsymbol e_{p_k}^k)\tr{},
        %
        \\\bs F_i^{k,k+1}\boldsymbol d &= \boldsymbol \phi_{k}(y_{k+1})\tr{} \boldsymbol \phi_{k+1}(y_{k+1})\boldsymbol d \\&= (\bs e^{k}_{p_k})\tr{} \bs e_{1}^{k+1}\bs d \\&= d_{1}(\boldsymbol e_{N_{k}}^{k})\tr{}.
	\end{align*}
	Hence, observe that 
	\begin{align*}
		&\bs P_k^{-1}\bs F_i^{kk} \bs M_k^{-1} \bs P_k \bs 1 = \bs P_k^{-1} \bs \phi_k(y_k)'\bs 1 = -\bs P_k^{-1}\bs F_i^{k,k+1} \bs M_k^{-1} \bs P_k \bs 1 = - \bs P_k^{-1}(\bs e_{p_k}^k)',
	\end{align*}
	for \(k=0,1,\dots,K-1\). 
	Similarly, for \(c_i<0\), 
	\begin{align*}
		&\bs P_k^{-1}\bs F_i^{kk} \bs M_k^{-1} \bs P_k \bs 1 = \bs P_k^{-1} \bs \phi_k(y_{k+1})'\bs 1 = -\bs P_k^{-1}\bs F_i^{k,k-1} \bs M_k^{-1} \bs P_k \bs 1 = - \bs P_k^{-1}(\bs e_{1}^k)',
	\end{align*}
	for \(k=1,\dots,K\).

	Now, with the above observations made, we first claim that, for \(c_i>0\), and \(k=0,1,...,K-1\), 
	\begin{align*}
		\sum_{j\in\calS}\mathfrak{\bs B}^{kk}_{ij}\bs 1 + \mathfrak{\bs B}^{kk+1}_{ij}\bs 1
		&=\sum_{j\in\calS}T_{ij}\bs I_{p_k}\bs 1 + c_i \bs P_k^{-1}(\bs F_i^{kk}+\bs G_k)\bs M_k^{-1}\bs P_k\boldsymbol 1 + c_i \bs P_k^{-1}\bs F_i^{k,k+1}\bs M_k^{-1}\bs P_k\boldsymbol 1 
		\\&=\bs 0.
	\end{align*}
	The first sum is zero since \(\bs T\) is a generator of a continuous-time Markov chain. This leaves the other two terms, which, using our observations, we get 
	\begin{align*}
		& c_i \bs P_k^{-1}(\bs F_i^{kk}+\bs G_k)\bs M_k^{-1}\bs P_k\boldsymbol 1 + c_i \bs P_k^{-1}\bs F_i^{k,k+1}\bs M_{k+1}^{-1}\bs P_{k+1}\boldsymbol 1
		\\&= c_i \bs P_k^{-1}\bs F_i^{kk} \bs M_k^{-1}\bs P_k\boldsymbol 1 + c_i \bs P_k^{-1}\bs G_k\bs M_k^{-1}\bs P_k\boldsymbol 1 + c_i \bs P_k^{-1}\bs F_i^{k,k+1}\bs M_{k+1}^{-1}\bs P_{k+1}\boldsymbol 1 
		\\&= \boldsymbol 0.
	\end{align*}
	For \(c_i>0\) and \(k=K\), 
	\begin{align*}
		&\sum_{j\in\calS}\mathfrak{\bs B}^{KK}_{ij}\bs 1 + \mathfrak{\bs B}^{K{K+1}}_{ij}\bs 1
		\\&= \sum_{j\in\calS}T_{ij}\bs I_{N_K}\bs 1-\sum_{j\in\calS_-} c_ip_{ij}^{K+1} \bs P_K^{-1}\bs F_i^{KK}\bs M_K^{-1}\bs P_K \bs 1 -\sum_{j\in\calS_{{K+1} }}c_ip_{ij}^{K+1} \bs P_K^{-1}\boldsymbol \phi_K(0)\tr{}\bs 1 
		\\&\quad{} + c_i \bs P_K^{-1}(\bs F_i^{KK}+\bs G_K)\bs M_K^{-1}\bs P_K\boldsymbol 1 
		\\&= -\sum_{j\in\calS_-} c_ip_{ij}^{K+1} \bs P_K^{-1}\bs F_i^{KK}\bs M_K^{-1}\bs P_K \bs 1 
		\\&{}\quad-\sum_{j\in\calS_{{K+1}}}c_ip_{ij}^{K+1} \bs P_K^{-1}\bs F_i^{KK}\bs M_K^{-1}\bs P_K\bs 1+ c_i \bs P_K^{-1}\bs F_i^{KK}\bs M_K^{-1}\bs P_K\boldsymbol 1
		\\&\quad{}+ c_i \bs P_K^{-1}\bs G_K\bs M_K^{-1}\bs P_K\boldsymbol 1
		%
		\\&= - c_i \bs P_K^{-1}\bs F_i^{KK}\bs M_K^{-1}\bs P_K \bs 1 + c_i \bs P_K^{-1}\bs F_i^{KK}\bs M_K^{-1}\bs P_K\boldsymbol 1 + c_i \bs P_K^{-1}\bs G_K\boldsymbol 1
		\\&= \bs 0.
	\end{align*}
	% Similarly, for \(c_i<0\), and row-vectors \(\boldsymbol b\) and \(\boldsymbol d\) of length \(p_k\) and \(N_{k-1}\), respectively, 
	% \begin{align*}
	% 	\bs F_i^{kk}\boldsymbol b &= \boldsymbol \phi^k(y_{k})\tr{} \boldsymbol \phi^k(y_{k})\boldsymbol b \\&= (\bs e^{k}_{1})\tr{} \bs e_{1}^{k}\bs b  \\&= b_{1}(\boldsymbol e_{1}^k)\tr{} 
	% 	%
	% 	\\\bs F_i^{k,k-1}\boldsymbol d &= -\boldsymbol \phi^{k}(y_{k})\tr{} \boldsymbol \phi^{k-1}(y_{k})\boldsymbol d \\&= -(\bs e^{k}_{1})\tr{} \bs e_{N_{k-1}}^{k-1}\bs d \\&= -d_{N_{k-1}}(\boldsymbol e_{1}^k)\tr{}.
	% 	\end{align*}

		Similarly, for \(c_i<0\) and \(k=1,...,K\), using the same arguments as before we have
	\begin{align*}
		\sum_{j\in\calS}\mathfrak{\bs B}^{kk}_{ij}\bs 1 + \mathfrak{\bs B}^{kk-1}_{ij}\bs 1
		&=\sum_{j\in\calS}T_{ij}\bs I_{p_k}\bs 1 + c_i \bs P_k^{-1}(\bs F_i^{kk}+\bs G_k)\bs M_k^{-1}\bs P_k\boldsymbol 1 + c_i \bs P_k^{-1}\bs F_i^{k,k-1}\bs M_k^{-1}\bs P_k\boldsymbol 1
		% \\&= \boldsymbol 0 + c_i \bs P_k^{-1}(\bs F_i^{kk}+\bs G_k)\bs M_k^{-1}\bs P_k\boldsymbol 1 + c_i \bs P_k^{-1}\bs F_i^{k,k+1}\bs M_{k-1}^{-1}\bs P_{k-1}\boldsymbol 1
		% \\&= c_i \bs P_k^{-1}(\bs F_i^{kk}+\bs G_k)\boldsymbol 1 + c_i \bs P_k^{-1}\bs F_i^{k,k-1}\boldsymbol 1
		% \\&= c_i \bs P_k^{-1}\bs F_i^{kk}\boldsymbol 1 + c_i \bs P_k^{-1}\bs G_k\boldsymbol 1 + c_i \bs P_k^{-1}\bs F_i^{k,k-1}\boldsymbol 1
		% \\&= c_i \bs P_k^{-1}(\boldsymbol e_{1}^k)\tr{} + \boldsymbol 0 + c_i \bs P_k^{-1}(-\boldsymbol e_{1}^k)\tr{}
		\\&= \boldsymbol 0.
	\end{align*}
	For \(c_i<0\) and \(k=K\), 
	\begin{align*}
		\sum_{j\in\calS}\mathfrak{\bs B}^{00}_{ij}\bs 1 + \mathfrak{\bs B}^{0{-1}}_{ij}\bs 1
		&= \sum_{j\in\calS}T_{ij}\bs I_{N_0}\bs 1-\sum_{j\in\calS_+} c_ip_{ij}^{-1} \bs P_0^{-1}\bs F_i^{00}\bs M_0^{-1}\bs P_0 \bs 1 -\sum_{j\in\calS_{{-1} }}c_ip_{ij}^{-1} \bs P_0^{-1}\boldsymbol \phi_0(0)\tr{}\bs 1 
		\\&\quad{} + c_i \bs P_0^{-1}(\bs F_i^{0,0}+\bs G_0)\bs M_0^{-1}\bs P_0\boldsymbol 1 
		% \\&= -\sum_{j\in\calS_+} c_ip_{ij}^{-1} \bs P_1^{-1}\bs F_i^{11}\bs M_1^{-1}\bs P_1 \bs 1 -\sum_{j\in\calS_{{-1} }}c_ip_{ij}^{-1} \bs P_1^{-1}\bs F_i^{11}\bs M_1^{-1}\bs P_1\bs 1+ c_i \bs P_1^{-1}\bs F_i^{1,1}\bs M_1^{-1}\bs P_1\boldsymbol 1
		% \\&\quad{}+ c_i \bs P_1^{-1}\bs G_1\bs M_1^{-1}\bs P_1\boldsymbol 1
		% %
		% \\&= - c_i \bs P_1^{-1}\bs F_i^{11}\bs M_1^{-1}\bs P_1 \bs 1 + c_i \bs P_1^{-1}\bs F_i^{1,1}\bs M_1^{-1}\bs P_1\boldsymbol 1 + c_i \bs P_1^{-1}\bs G_1\boldsymbol 1
		\\&= \bs 0.
	\end{align*}

	This just leaves the boundaries. For the lower boundary,
	\begin{align*}
		\mathfrak{\bs B}^{{-1},{-1}}\boldsymbol 1 +  {  {\mathfrak{\bs B}}}^{{-1}0}\boldsymbol 1 
		&= \bs T_{{-1},{-1}}\boldsymbol 1 + \left[\bs T_{{-1}+}\otimes\left( \boldsymbol\phi_0(0)\bs M_0^{-1}\bs P_0\right)\right]\boldsymbol 1. 
		\intertext{ Swapping the order of summation and recalling \(\bs M_k^{-1}\bs P_k\boldsymbol 1=\boldsymbol 1\) then this is equal to}
		\bs T_{{-1},{-1}}\boldsymbol 1 + \left[\bs T_{{-1}+}\otimes\left( \boldsymbol\phi_0(0)\bs M_0^{-1}\bs P_0\right)\boldsymbol 1\right]\boldsymbol 1 
		%
		&= \bs T_{{-1},{-1}}\boldsymbol 1 + \left[\bs T_{{-1}+}\otimes \boldsymbol e_1^0\bs 1\right]\bs 1
		\\&= \bs T_{{-1},{-1}}\boldsymbol 1 + \left[\bs T_{{-1}+}\otimes \boldsymbol 1\right]\bs 1
		\\&= \bs T_{{-1},{-1}}\boldsymbol 1 + \bs T_{{-1}+}\bs 1
		%
		\\&= \boldsymbol 0.
	\end{align*}	
	For the upper boundary,
	\begin{align*}
		\mathfrak{\bs B}^{{K+1},{K+1}}\boldsymbol 1 +  {  {\mathfrak{\bs B}}}^{{K+1} K}\boldsymbol 1 
		&= \bs T_{{K+1},{K+1}}\boldsymbol 1 + [\bs T_{{K+1}-}\otimes( \boldsymbol\phi_K(b)\bs M_K^{-1}\bs P_K)]\boldsymbol 1.
		\intertext{Swapping the order of summation and recalling \(\bs M_k^{-1}\bs P_k\boldsymbol 1=\boldsymbol 1\) then this is equal to}
        \bs T_{{K+1},{K+1}}\boldsymbol 1 + [\bs T_{{K+1}-}\otimes( \boldsymbol\phi_K(b)\bs M_K^{-1}\bs P_K)\bs 1]\boldsymbol 1 
		%
		%\\&%= T_{{K+1},{K+1}}\boldsymbol 1 + [T_{{K+1}-}\otimes \boldsymbol\phi^K(b)\bs 1]\boldsymbol 1
		&= \bs T_{{K+1},{K+1}}\boldsymbol 1 + [\bs T_{{K+1}-}\otimes\bs e^K_{N_K}\bs 1]\boldsymbol 1
		\\&= \bs T_{{K+1},{K+1}}\boldsymbol 1 + [\bs T_{{K+1}-}\otimes \bs e^K_{N_K}]\bs 1
		\\&= \bs T_{{K+1},{K+1}}\boldsymbol 1 + \bs T_{{K+1}-}\bs 1
		%
		\\&= \boldsymbol 0.
	\end{align*}

>>>>

	T_{ii}\bs I_{p_0} + c_i\bs P_0^{-1}(\bs F_i^{00}+\bs G_0)\bs M_0^{-1}\bs P_0 & i = j, \\
T_{ij}\bs I_{p_0} - c_ip_{ij}^{-1} 1(c_i<0)\bs F_i^{00}\bs M_0^{-1}\bs P_0 & i \neq j,

@@

	T_{ii}\bs I_{p_K} + c_i\bs P_K^{-1}(\bs F_i^{KK}+\bs G_K)\bs M_K^{-1}\bs P_K & i = j, \\
T_{ij}\bs I_{p_K} + c_ip_{ij}^{K+1} 1(c_i>0)\bs P_K^{-1}\bs F_i^{KK}\bs M_K^{-1}\bs P_K & i \neq j,

@@

\begin{lem}
	If \(\{\phi^r_k(x)\}_{r\in\{1,...,p_k\}}\), are chosen as the Lagrange interpolating polynomials on \(\mathcal D_k\), \(k\in\mathcal K^\circ\), then the matrix \( {  {\mathfrak{\bs B}}}\) has zero row-sums. 
\end{lem}
\begin{proof}
	First we make numerous algebraic observations. Let \(\boldsymbol 1\) and \(\boldsymbol 0\) be column vectors of ones and zeros, respectively, with an appropriate length depending on the context. Using Property 1, observe that 
	\begin{align*}
        \bs M_k\boldsymbol 1 &= \left(\sum_{s=1}^{p_k} \int_{x\in\calD_k}\phi^r_k(x)\phi_s^k(x)\wrt x\right)_{r\in\{1,...,p_k\}}\tr{}
	%
        \\&= \left(\int_{x\in\calD_k}\phi^r_k(x)\sum_{s=1}^{p_k} \phi_s^k(x)\wrt x \right)_{r\in\{1,...,p_k\}} \tr{}
        %
        \\&= \left(\int_{x\in\calD_k}\phi^r_k(x)\wrt x\right)_{r\in\{1,...,p_k\}} \tr{}
        %
        \\&= \bs P_k\boldsymbol 1,
	\end{align*}
	hence \(\bs M_k^{-1}\bs P_k\boldsymbol 1=\boldsymbol 1\). Also, 
	\begin{align*}
        \bs G_k\bs M_k^{-1}\bs P_k\boldsymbol 1 = \bs G_k\boldsymbol 1 &= \left(\sum_{s=1}^{p_k} \int_{x\in\calD_k}\phi^r_k(x)\cfrac{\wrt }{\wrt x}\phi_k^s(x)\wrt x\right)_{r\in\{1,...,p_k\}} \tr{}
	%
        \\&= \left(\int_{x\in\calD_k}\phi^r_k(x)\cfrac{\wrt }{\wrt x}\sum_{s=1}^{p_k} \phi_k^s(x)\wrt x \right)_{r\in\{1,...,p_k\}} \tr{}
	%
        \\&= \left(\int_{x\in\calD_k}\phi^r_k(x)\cfrac{\wrt }{\wrt x}1\wrt x\right)_{r\in\{1,...,p_k\}} \tr{}
	%
        \\&= \boldsymbol 0,
	\end{align*}
	where we have again used Property 1. Consider \(c_i>0\) and let \(\boldsymbol b\) and \(\boldsymbol d\) be arbitrary row-vectors of length \(p_k\) and \(p_{k+1}\), respectively. By Property 2, for \(k\in\mathcal K^\circ,\)
	\begin{align*}
        \bs F_i^{kk}\boldsymbol b &= -\boldsymbol \phi_k(y_{k+1})\tr{} \boldsymbol \phi_k(y_{k+1})\boldsymbol b \\&= -(\bs e^k_{p_k})\tr{} \bs e_{p_k}^k\bs b \\&= -b_{p_k}(\boldsymbol e_{p_k}^k)\tr{},
        %
        \\\bs F_i^{k,k+1}\boldsymbol d &= \boldsymbol \phi_{k}(y_{k+1})\tr{} \boldsymbol \phi_{k+1}(y_{k+1})\boldsymbol d \\&= (\bs e^{k}_{p_k})\tr{} \bs e_{1}^{k+1}\bs d \\&= d_{1}(\boldsymbol e_{p_{k}}^{k})\tr{}.
	\end{align*}
	Hence, observe that 
	\begin{align*}
		&\bs P_k^{-1}\bs F_i^{kk} \bs M_k^{-1} \bs P_k \bs 1 = \bs P_k^{-1} \bs \phi_k(y_k)'\bs 1 = -\bs P_k^{-1}\bs F_i^{k,k+1} \bs M_k^{-1} \bs P_k \bs 1 = - \bs P_k^{-1}(\bs e_{p_k}^k)',
	\end{align*}
	for \(k=0,1,\dots,K-1\). 
	Similarly, for \(c_i<0\), 
	\begin{align*}
		&\bs P_k^{-1}\bs F_i^{kk} \bs M_k^{-1} \bs P_k \bs 1 = \bs P_k^{-1} \bs \phi_k(y_{k+1})'\bs 1 = -\bs P_k^{-1}\bs F_i^{k,k-1} \bs M_k^{-1} \bs P_k \bs 1 = - \bs P_k^{-1}(\bs e_{1}^k)',
	\end{align*}
	for \(k=1,\dots,K\).

	Now, with the above observations made, we first claim that, for \(c_i>0\), and \(k=0,1,...,K-1\), 
	\begin{align*}
		\sum_{j\in\calS}\mathfrak{\bs B}^{kk}_{ij}\bs 1 + \mathfrak{\bs B}^{kk+1}_{ij}\bs 1
		&=\sum_{j\in\calS}T_{ij}\bs I_{p_k}\bs 1 + c_i \bs P_k^{-1}(\bs F_i^{kk}+\bs G_k)\bs M_k^{-1}\bs P_k\boldsymbol 1 + c_i \bs P_k^{-1}\bs F_i^{k,k+1}\bs M_k^{-1}\bs P_k\boldsymbol 1 
		\\&=\bs 0.
	\end{align*}
	The first sum is zero since \(\bs T\) is a generator of a continuous-time Markov chain. This leaves the other two terms, which, using our observations, we get 
	\begin{align*}
		& c_i \bs P_k^{-1}(\bs F_i^{kk}+\bs G_k)\bs M_k^{-1}\bs P_k\boldsymbol 1 + c_i \bs P_k^{-1}\bs F_i^{k,k+1}\bs M_{k+1}^{-1}\bs P_{k+1}\boldsymbol 1
		\\&= c_i \bs P_k^{-1}\bs F_i^{kk} \bs M_k^{-1}\bs P_k\boldsymbol 1 + c_i \bs P_k^{-1}\bs G_k\bs M_k^{-1}\bs P_k\boldsymbol 1 + c_i \bs P_k^{-1}\bs F_i^{k,k+1}\bs M_{k+1}^{-1}\bs P_{k+1}\boldsymbol 1 
		\\&= \boldsymbol 0.
	\end{align*}
	For \(c_i>0\) and \(k=K\), 
	\begin{align*}
		&\sum_{j\in\calS}\mathfrak{\bs B}^{KK}_{ij}\bs 1 + \mathfrak{\bs B}^{K{K+1}}_{ij}\bs 1
		\\&= \sum_{j\in\calS}T_{ij}\bs I_{p_K}\bs 1-\sum_{j\in\calS_-} c_ip_{ij}^{K+1} \bs P_K^{-1}\bs F_i^{KK}\bs M_K^{-1}\bs P_K \bs 1 -\sum_{j\in\calS_{{K+1} }}c_ip_{ij}^{K+1} \bs P_K^{-1}\boldsymbol \phi_K(0)\tr{}\bs 1 
		\\&\quad{} + c_i \bs P_K^{-1}(\bs F_i^{KK}+\bs G_K)\bs M_K^{-1}\bs P_K\boldsymbol 1 
		\\&= -\sum_{j\in\calS_-} c_ip_{ij}^{K+1} \bs P_K^{-1}\bs F_i^{KK}\bs M_K^{-1}\bs P_K \bs 1 
		\\&{}\quad-\sum_{j\in\calS_{{K+1}}}c_ip_{ij}^{K+1} \bs P_K^{-1}\bs F_i^{KK}\bs M_K^{-1}\bs P_K\bs 1+ c_i \bs P_K^{-1}\bs F_i^{KK}\bs M_K^{-1}\bs P_K\boldsymbol 1
		\\&\quad{}+ c_i \bs P_K^{-1}\bs G_K\bs M_K^{-1}\bs P_K\boldsymbol 1
		%
		\\&= - c_i \bs P_K^{-1}\bs F_i^{KK}\bs M_K^{-1}\bs P_K \bs 1 + c_i \bs P_K^{-1}\bs F_i^{KK}\bs M_K^{-1}\bs P_K\boldsymbol 1 + c_i \bs P_K^{-1}\bs G_K\boldsymbol 1
		\\&= \bs 0.
	\end{align*}
	% Similarly, for \(c_i<0\), and row-vectors \(\boldsymbol b\) and \(\boldsymbol d\) of length \(p_k\) and \(p_{k-1}\), respectively, 
	% \begin{align*}
	% 	\bs F_i^{kk}\boldsymbol b &= \boldsymbol \phi^k(y_{k})\tr{} \boldsymbol \phi^k(y_{k})\boldsymbol b \\&= (\bs e^{k}_{1})\tr{} \bs e_{1}^{k}\bs b  \\&= b_{1}(\boldsymbol e_{1}^k)\tr{} 
	% 	%
	% 	\\\bs F_i^{k,k-1}\boldsymbol d &= -\boldsymbol \phi^{k}(y_{k})\tr{} \boldsymbol \phi^{k-1}(y_{k})\boldsymbol d \\&= -(\bs e^{k}_{1})\tr{} \bs e_{p_{k-1}}^{k-1}\bs d \\&= -d_{p_{k-1}}(\boldsymbol e_{1}^k)\tr{}.
	% 	\end{align*}

		Similarly, for \(c_i<0\) and \(k=1,...,K\), using the same arguments as before we have
	\begin{align*}
		\sum_{j\in\calS}\mathfrak{\bs B}^{kk}_{ij}\bs 1 + \mathfrak{\bs B}^{kk-1}_{ij}\bs 1
		&=\sum_{j\in\calS}T_{ij}\bs I_{p_k}\bs 1 + c_i \bs P_k^{-1}(\bs F_i^{kk}+\bs G_k)\bs M_k^{-1}\bs P_k\boldsymbol 1 + c_i \bs P_k^{-1}\bs F_i^{k,k-1}\bs M_k^{-1}\bs P_k\boldsymbol 1
		% \\&= \boldsymbol 0 + c_i \bs P_k^{-1}(\bs F_i^{kk}+\bs G_k)\bs M_k^{-1}\bs P_k\boldsymbol 1 + c_i \bs P_k^{-1}\bs F_i^{k,k+1}\bs M_{k-1}^{-1}\bs P_{k-1}\boldsymbol 1
		% \\&= c_i \bs P_k^{-1}(\bs F_i^{kk}+\bs G_k)\boldsymbol 1 + c_i \bs P_k^{-1}\bs F_i^{k,k-1}\boldsymbol 1
		% \\&= c_i \bs P_k^{-1}\bs F_i^{kk}\boldsymbol 1 + c_i \bs P_k^{-1}\bs G_k\boldsymbol 1 + c_i \bs P_k^{-1}\bs F_i^{k,k-1}\boldsymbol 1
		% \\&= c_i \bs P_k^{-1}(\boldsymbol e_{1}^k)\tr{} + \boldsymbol 0 + c_i \bs P_k^{-1}(-\boldsymbol e_{1}^k)\tr{}
		\\&= \boldsymbol 0.
	\end{align*}
	For \(c_i<0\) and \(k=K\), 
	\begin{align*}
		\sum_{j\in\calS}\mathfrak{\bs B}^{00}_{ij}\bs 1 + \mathfrak{\bs B}^{0{-1}}_{ij}\bs 1
		&= \sum_{j\in\calS}T_{ij}\bs I_{p_0}\bs 1-\sum_{j\in\calS_+} c_ip_{ij}^{-1} \bs P_0^{-1}\bs F_i^{00}\bs M_0^{-1}\bs P_0 \bs 1 -\sum_{j\in\calS_{{-1} }}c_ip_{ij}^{-1} \bs P_0^{-1}\boldsymbol \phi_0(0)\tr{}\bs 1 
		\\&\quad{} + c_i \bs P_0^{-1}(\bs F_i^{0,0}+\bs G_0)\bs M_0^{-1}\bs P_0\boldsymbol 1 
		% \\&= -\sum_{j\in\calS_+} c_ip_{ij}^{-1} \bs P_1^{-1}\bs F_i^{11}\bs M_1^{-1}\bs P_1 \bs 1 -\sum_{j\in\calS_{{-1} }}c_ip_{ij}^{-1} \bs P_1^{-1}\bs F_i^{11}\bs M_1^{-1}\bs P_1\bs 1+ c_i \bs P_1^{-1}\bs F_i^{1,1}\bs M_1^{-1}\bs P_1\boldsymbol 1
		% \\&\quad{}+ c_i \bs P_1^{-1}\bs G_1\bs M_1^{-1}\bs P_1\boldsymbol 1
		% %
		% \\&= - c_i \bs P_1^{-1}\bs F_i^{11}\bs M_1^{-1}\bs P_1 \bs 1 + c_i \bs P_1^{-1}\bs F_i^{1,1}\bs M_1^{-1}\bs P_1\boldsymbol 1 + c_i \bs P_1^{-1}\bs G_1\boldsymbol 1
		\\&= \bs 0.
	\end{align*}

	This just leaves the boundaries. For the lower boundary,
	\begin{align*}
		\mathfrak{\bs B}^{{-1},{-1}}\boldsymbol 1 +  {  {\mathfrak{\bs B}}}^{{-1}0}\boldsymbol 1 
		&= \bs T_{{-1},{-1}}\boldsymbol 1 + \left[\bs T_{{-1}+}\otimes\left( \boldsymbol\phi_0(0)\bs M_0^{-1}\bs P_0\right)\right]\boldsymbol 1. 
		\intertext{ Swapping the order of summation and recalling \(\bs M_k^{-1}\bs P_k\boldsymbol 1=\boldsymbol 1\) then this is equal to}
		\bs T_{{-1},{-1}}\boldsymbol 1 + \left[\bs T_{{-1}+}\otimes\left( \boldsymbol\phi_0(0)\bs M_0^{-1}\bs P_0\right)\boldsymbol 1\right]\boldsymbol 1 
		%
		&= \bs T_{{-1},{-1}}\boldsymbol 1 + \left[\bs T_{{-1}+}\otimes \boldsymbol e_1^0\bs 1\right]\bs 1
		\\&= \bs T_{{-1},{-1}}\boldsymbol 1 + \left[\bs T_{{-1}+}\otimes \boldsymbol 1\right]\bs 1
		\\&= \bs T_{{-1},{-1}}\boldsymbol 1 + \bs T_{{-1}+}\bs 1
		%
		\\&= \boldsymbol 0.
	\end{align*}	
	For the upper boundary,
	\begin{align*}
		\mathfrak{\bs B}^{{K+1},{K+1}}\boldsymbol 1 +  {  {\mathfrak{\bs B}}}^{{K+1} K}\boldsymbol 1 
		&= \bs T_{{K+1},{K+1}}\boldsymbol 1 + [\bs T_{{K+1}-}\otimes( \boldsymbol\phi_K(b)\bs M_K^{-1}\bs P_K)]\boldsymbol 1.
		\intertext{Swapping the order of summation and recalling \(\bs M_k^{-1}\bs P_k\boldsymbol 1=\boldsymbol 1\) then this is equal to}
        \bs T_{{K+1},{K+1}}\boldsymbol 1 + [\bs T_{{K+1}-}\otimes( \boldsymbol\phi_K(b)\bs M_K^{-1}\bs P_K)\bs 1]\boldsymbol 1 
		%
		%\\&%= T_{{K+1},{K+1}}\boldsymbol 1 + [T_{{K+1}-}\otimes \boldsymbol\phi^K(b)\bs 1]\boldsymbol 1
		&= \bs T_{{K+1},{K+1}}\boldsymbol 1 + [\bs T_{{K+1}-}\otimes\bs e^K_{p_K}\bs 1]\boldsymbol 1
		\\&= \bs T_{{K+1},{K+1}}\boldsymbol 1 + [\bs T_{{K+1}-}\otimes \bs e^K_{p_K}]\bs 1
		\\&= \bs T_{{K+1},{K+1}}\boldsymbol 1 + \bs T_{{K+1}-}\bs 1
		%
		\\&= \boldsymbol 0.
	\end{align*}
